State and Parameter Estimation for Spatio-Temporal Neural Fields

### 2010-04-18 ltx/Journal of Neuroengineering/StateAndParameterEstimationNeuralFields_JoNE.tex
more figures for freq analysis
updates to figures

%<-comment out this for checking equations
\usepackage{graphicx, algorithm, algorithmicx, algpseudocode,epsfig} 
\usepackage{color} 
\usepackage[tight,scriptsize]{subfigure}

@@

The sensors were modelled such that they were spaced in a regular square grid, where the number of sensors was 100, sensor width $\sigma^2_m$ was 1.44 which equals $2$~mm full width at half maximum, with spacing $\Delta_y$ equal to $2.22$~mm. This arrangement modelled the recording as having some cross talk, which is typical from neurophysiological recordings. Note, sensor design to guarantee representation of the field can be achieved using the frequency analysis from section~\ref{} given access to the true field. \omg{From frequency analysis the separation is $2.77$, with $\rho = 2$ (note same as basis function).} 
\begin{figure}
	\begin{center}
		\includegraphics[scale=0.4]{./Graph/ExperimentFigure.jpg} 
	\end{center}
	\caption{Example of experimental design and model output. \textbf{A}. Example of the neural field with sensors. The centres of the sensors are shown by crossed and the sensor widths ($1/2$ height of Gaussian) are shown by the circles. \textbf{B} Example of data generated by the model through the observations. \textbf{C}. Power spectral density of the data generated by an observation showing the typical $1/f$ characteristic of iEEG.} \label{fig:FrequencyAnalysis} 
\end{figure}

@@

The spatial frequency of the observations is shown in figure~\ref{}. The peak power of the spatial frequency of the observations was approximately $30$~dB. The cut-off frequency was taken to correspond to \omg{??} of the peak pwoer which was approximately $15$~dB. This provided a conservative The oversampling parameter $\rho=2$. From equation~\ref{}, this gives a minimum distance between basis functions of $2.7$ to satisfy Shannon's sampling criterion. \todo{maybe from Parham's derivation... From equation~\ref{} the width was calculated to be... or...}. The width of the basis functions was chosen such that they had sufficient overlap to represent the dynamic field.
\begin{figure}
	\begin{center}
		\subfigure[][]{
		\includegraphics[scale=0.2]{./Graph/kernel.pdf}} \subfigure[][]{
		\includegraphics[scale=0.2]{./Graph/field.pdf}} \subfigure[][]{
		\includegraphics[scale=0.2]{./Graph/filtered.pdf}} 
	\end{center}
	\caption{Example of experimental design and model output. \textbf{A}. Example of the neural field with sensors. The centres of the sensors are shown by crossed and the sensor widths ($1/2$ height of Gaussian) are shown by the circles. \textbf{B} Example of data generated by the model through the observations. \textbf{C}. Power spectral density of the data generated by an observation showing the typical $1/f$ characteristic of iEEG.} \label{fig:ExampleFieldAndSensorsDataAndPSD} 
\end{figure}
Following this, the distance between basis function, $\Delta_b$, was set to $2.5$ and the basis function width, $\sigma_{\phi}^2$, was set to 3.6, 3.16 mm full width at half maximum. Analysis said 3.9 from Parham's derivation, but 3.6 still overlaps and allows more high frequency details to be represented.

>>>>

%<-comment out this for checking equations
\usepackage{graphicx,epsfig}
\usepackage{algorithm, algorithmicx, algpseudocode} 
\usepackage{color} 
\usepackage[tight,scriptsize]{subfigure}

@@

The sensors were modelled such that they were spaced in a regular square grid, where the number of sensors was 100, sensor width $\sigma^2_m$ was 1.44 which equals $2$~mm full width at half maximum, with spacing $\Delta_y$ equal to $2.22$~mm. This arrangement modelled the recording as having some cross talk, which is typical from neurophysiological recordings. Note, sensor design to guarantee representation of the field can be achieved using the frequency analysis from section~\ref{} given access to the true field. \omg{From frequency analysis the separation is $2.77$, with $\rho = 2$ (note same as basis function).} 
% \begin{figure}
% 	\begin{center}
		\includegraphics[scale=0.4]{./Graph/ExperimentFigure.eps} 
% 	\end{center}
% 	\caption{Example of experimental design and model output. \textbf{A}. Example of the neural field with sensors. The centres of the sensors are shown by crossed and the sensor widths ($1/2$ height of Gaussian) are shown by the circles. \textbf{B} Example of data generated by the model through the observations. \textbf{C}. Power spectral density of the data generated by an observation showing the typical $1/f$ characteristic of iEEG.} \label{fig:FrequencyAnalysis} 
% \end{figure}

@@

The spatial frequency of the observations is shown in figure~\ref{}. The peak power of the spatial frequency of the observations was approximately $30$~dB. The cut-off frequency was taken to correspond to \omg{??} of the peak pwoer which was approximately $15$~dB. This provided a conservative The oversampling parameter $\rho=2$. From equation~\ref{}, this gives a minimum distance between basis functions of $2.7$ to satisfy Shannon's sampling criterion. \todo{maybe from Parham's derivation... From equation~\ref{} the width was calculated to be... or...}. The width of the basis functions was chosen such that they had sufficient overlap to represent the dynamic field.

\begin{figure}
	\begin{center}
		\includegraphics[scale=0.5,angle=-90]{./Graph/FreqAnalysis.eps}
	\end{center}
	\caption{..... \textbf{A}. Field. \textbf{B} Field filtered using sensor kernel. \textbf{C}. Observations.} \label{fig:ExampleFieldAndSensorsDataAndPSD} 
\end{figure}
Following this, the distance between basis function, $\Delta_b$, was set to $2.5$ and the basis function width, $\sigma_{\phi}^2$, was set to 3.6, 3.16 mm full width at half maximum. Analysis said 3.9 from Parham's derivation, but 3.6 still overlaps and allows more high frequency details to be represented.
